Quantum Computing and its Implications on Digital Security

### 2021-12-13 paper.tex
feat: Improve Shor's algorithm

% Look into paper for this. The paper has a perfect level for our own research.
\begin{subsection}{Shor's algorithm}
Shor's algorithm is a polynomial-time quantum computer algorithm for integer factorization.
Essentially it solves the following problem: 
Given an integer $N$m find its prime factors. 
On a quantum computer, to factor an integer $N$, 
Shor's algorithm runs in polynomial time. 
Using quantum gates demonstrates, 
that integer-factorization can be solved on a quantum computer an is consequently in the complexity class BQP, 
which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $1/3$ for all instances. 
This algorithm is almost exponentially faster than the most efficient known classical factoring algorithm, the general number field sieve which is the most efficient known factoring algorithm on regular computers. 
The efficiency of Shor's algorithm is due to the efficiency of the quantum Fourier transform and modular exponentiation by repeated squearings. 
If a quantum computer with a sufficient number of qubits could operate without succumbing to quantum noise and other quantum-decoherence phenomena, 
Shor's algorithm could be used to break public-key cryptography schemes, 
such as the RSA scheme or the Diffie-Hellman key exchange. That these algorithms could be vulnerable was already stated by Kirsch in 2015
\cite{Kirsch2015QuantumCT}.

So far, the largest number factorized using Shor's algorithm, 
as of 2019 is the number 21 factored back in 2012 by Martín-López et al \cite{article}. 
The integer 35 was attempted in 2019 on an IBM Q System One, 
but the algorithm failed.

% Eventually add math for Shor's algorithm
\end{subsection}

>>>>

\begin{subsection}{Shor's algorithm}
Shor's algorithm is a quantum computer algorithm and got developed by Peter Shor in 1994.
Essentially, it can find the prime factors of an integer in the complexity class BQP,
which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $\frac{1}{3}$ for all instances. 
Shor's algorithm is nearly exponentially faster than the general number field sieve, which is the most efficient known classical factoring algorithm.
The efficiency of the quantum Fourier transform which, as earlier discussed, can be caluclated using e.g. an ion trap quantum computer, is responsible for the efficiency of Shor's algorithm.
The algorithm is generally capable to break current public-key cryptography mechanisms as RSA or the Diffie-Hellman key exchange if the quantum computer could operate with little noise. 
That these algorithms could be vulnerable was already stated by Kirsch in 2015
\cite{Kirsch2015QuantumCT}.

Bone and Castro \cite{Bone} describe the workings of Shor's algorithm as follows. First, a memory register is placed into a superposition of all its possible states. Think of all possible permutations of $n$ bits existing in parallel.
A calculation performed with Shor's algorithm can be thought of as computations done in parallel for every of the permutations generated before. 
They then describe the mathematics performed on the registers: 
\begin{itemize} 
    \item N describes the integer to be factorized
    \item X is a random number in range $1 < X < N-1$
    \item X is raised to one of the permutations generated earlier.
    \item The remainder of this operation is placed in a second register. The first register contains the permutation.
\end{itemize}
After performing these operations on all permutations, it is noticable that the contents of the second register repeat e.g. for $N = 15$ the repeating sequence would be $1,2,4,8,1,2,4...$.
Now the frequency of repetition can be calculated by using a complex operation on the second register and the looking at the contents which causes the results from every permutation to interfere. A possible prime factor can then be calculated by using the frequency of repetition $f$:
\begin{equation}
Factor P = X^{\frac{f}{2}}-1
\end{equation}
The inteference that provides $f$ will lead to the correct answer with a high probability as incorrect answers cancel each other out when interfering. This cannot be guaranteed! Checking that the resulting number is correct can be achieved by performing a simple multiplication. Repeating the process for different random values X has then a high chance of revealing all prime factors.

So far, the largest number factorized using Shor's algorithm, 
as of 2019 is the number 21 factored back in 2012 by Martín-López et al \cite{article}. 
The integer 35 was attempted in 2019 on an IBM Q System One, 
but the algorithm failed. 
\end{subsection}
